On the Minimum Core Mass for Giant Planet Formation through Kelvin-Helmholtz Contraction

### 2013-02-19 tex/draft/draft2.tex
draft updated with new figs

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/cumul_coolingtime_vs_Matm_10au_mu235.pdf}
%\vspace{-0.5in}
\caption{Time evolution as a function of atmosphere mass for a range of core masses. The circles mark the time when runaway accretion is initiated.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/coolingtime_vs_Mc_10au_new.pdf}
%\vspace{-0.5in}
\caption{Time evolution for atmospheres with different adiabatic indices and mean molecular weight. A typical protoplanetary disk life time is plotted for comparison.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mcrit_vs_a_3Myrs_new2.pdf}
%\vspace{-0.5in}
\caption{The minimum core mass for an atmosphere to become ÔcriticalÕ within the lifetime of the disk as a function of semi-major axis, for different adiabatic indices and molecular weight of the nebular gas.}
\end{figure}

@@

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.52\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/cumul_coolingtime_vs_Matm_10au_mu235.pdf}
%\vspace{-0.5in}
\caption{Time evolution as a function of atmosphere mass for a range of core masses. The circles mark the time when runaway accretion is initiated.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.48\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/coolingtime_vs_Mc_10au.pdf}
%\vspace{-0.5in}
\caption{Time evolution for atmospheres with different adiabatic indices and mean molecular weight. A typical protoplanetary disk life time is plotted for comparison.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mcrit_vs_a_3Myrs_new.pdf}
%\vspace{-0.5in}
\caption{The minimum core mass for an atmosphere to become ÔcriticalÕ within the lifetime of the disk as a function of semi-major axis, for different adiabatic indices and molecular weight of the nebular gas.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mcrit_vs_a_3Myrs_opacity.pdf}
%\vspace{-0.5in}
\caption{Opacity effect on critical core mass.}
\end{figure}
